---
title: "Online Retail Sales Analysis"
subtitle: "Revenue Trends, Product Performance, Sales Velocity & Demand Forecasting"
author: "Shawn | Lailara LLC"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Contents"
    toc-location: left
    theme: flatly
    highlight-style: github
    code-fold: true
    code-summary: "Show code"
    self-contained: true
    fig-width: 10
    fig-height: 5
    df-print: kable
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 10
    fig-height: 5
    geometry: margin=1in
    colorlinks: true
execute:
  echo: true
  warning: false
  message: false
  cache: false
---

```{r setup}
library(tidyverse)
library(lubridate)
library(scales)
library(kableExtra)
library(forecast)
library(ggrepel)
library(patchwork)

# ── Theme ────────────────────────────────────────────────────────────────────
retail_theme <- theme_minimal(base_size = 12) +
  theme(
    plot.title       = element_text(face = "bold", size = 14, color = "#1F3864"),
    plot.subtitle    = element_text(size = 11, color = "#555555"),
    plot.caption     = element_text(size = 8, color = "#888888", hjust = 0),
    axis.title       = element_text(size = 10, color = "#333333"),
    axis.text        = element_text(size = 9,  color = "#444444"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "#EEEEEE"),
    legend.position  = "bottom",
    legend.title     = element_text(size = 9),
    strip.text       = element_text(face = "bold", size = 10)
  )

theme_set(retail_theme)

PALETTE  <- c("#1F3864","#2E86AB","#A23B72","#F18F01","#C73E1D","#3B1F2B","#44BBA4")
NAVY     <- "#1F3864"
TEAL     <- "#44BBA4"
ORANGE   <- "#F18F01"
RED      <- "#C73E1D"
```

---

## 1 · Data Overview

```{r load-data}
# ── Load ─────────────────────────────────────────────────────────────────────
# Supports both .xlsx (original UCI file) and .csv (sample/testing)
data_xlsx <- here::here("data", "online_retail.xlsx")
data_csv  <- here::here("data", "online_retail.csv")

if (file.exists(data_xlsx)) {
  raw <- readxl::read_excel(data_xlsx)
} else if (file.exists(data_csv)) {
  raw <- read_csv(data_csv, show_col_types = FALSE)
} else {
  stop("No data file found. See README for download instructions.")
}

# ── Clean ─────────────────────────────────────────────────────────────────────
retail <- raw |>
  rename_with(tolower) |>
  rename(
    invoice_no   = invoiceno,
    stock_code   = stockcode,
    description  = description,
    quantity     = quantity,
    invoice_date = invoicedate,
    unit_price   = unitprice,
    customer_id  = customerid,
    country      = country
  ) |>
  mutate(
    invoice_date = as_datetime(invoice_date),
    date         = as_date(invoice_date),
    year         = year(invoice_date),
    month        = month(invoice_date, label = TRUE, abbr = TRUE),
    week         = floor_date(date, "week"),
    month_floor  = floor_date(date, "month"),
    is_cancel    = str_starts(invoice_no, "C"),
    revenue      = quantity * unit_price
  )

# ── Summaries for callouts ────────────────────────────────────────────────────
n_raw        <- nrow(retail)
n_cancel     <- sum(retail$is_cancel)
n_missing_cust <- sum(is.na(retail$customer_id))
date_min     <- min(retail$date)
date_max     <- max(retail$date)

# Remove cancellations and bad rows for analysis
clean <- retail |>
  filter(!is_cancel, quantity > 0, unit_price > 0)

n_clean      <- nrow(clean)
n_products   <- n_distinct(clean$stock_code)
n_customers  <- n_distinct(clean$customer_id, na.rm = TRUE)
n_countries  <- n_distinct(clean$country)
total_rev    <- sum(clean$revenue)
```

This dataset contains all transactions from a UK-based online gift retailer between
**`r format(date_min, "%B %d, %Y")`** and **`r format(date_max, "%B %d, %Y")`**.
The company's customer base is predominantly wholesale buyers.

::: {.callout-note}
## Dataset at a Glance
- **`r comma(n_raw)`** raw transaction rows across **`r n_countries`** countries
- **`r comma(n_cancel)`** cancellation records removed (`r percent(n_cancel/n_raw, 0.1)` of total)
- **`r comma(n_missing_cust)`** rows with no CustomerID (`r percent(n_missing_cust/n_raw, 0.1)`)
- **`r comma(n_clean)`** rows retained for analysis
- **`r comma(n_products)`** distinct products · **`r comma(n_customers)`** identified customers
- **£`r comma(total_rev, accuracy=1)`** total revenue in analysis window
:::

```{r data-quality-table}
# Missing value summary
tibble(
  Field       = c("InvoiceNo","StockCode","Description","Quantity",
                  "InvoiceDate","UnitPrice","CustomerID","Country"),
  `Non-Null`  = map_int(raw, ~ sum(!is.na(.))),
  `Null Count`= map_int(raw, ~ sum(is.na(.))),
  `Null %`    = map_chr(raw, ~ percent(mean(is.na(.)), 0.1))
) |>
  kbl(caption = "Field-Level Completeness") |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE) |>
  column_spec(4, bold = TRUE,
              color = ifelse(
                map_dbl(raw, ~ mean(is.na(.))) > 0.1, RED, "#333333"
              ))
```

---

## 2 · Revenue Trends

```{r monthly-revenue}
monthly_rev <- clean |>
  group_by(month_floor) |>
  summarise(
    revenue    = sum(revenue),
    n_orders   = n_distinct(invoice_no),
    n_items    = sum(quantity),
    .groups    = "drop"
  )

peak <- monthly_rev |> slice_max(revenue, n = 1)

ggplot(monthly_rev, aes(x = month_floor, y = revenue)) +
  geom_area(fill = NAVY, alpha = 0.12) +
  geom_line(color = NAVY, linewidth = 1.1) +
  geom_point(color = NAVY, size = 2.5) +
  geom_point(data = peak, color = ORANGE, size = 4) +
  geom_label(
    data     = peak,
    aes(label = paste0("Peak\n£", comma(revenue, accuracy = 1))),
    nudge_y  = max(monthly_rev$revenue) * 0.08,
    size     = 3, fill = "white", color = ORANGE, fontface = "bold"
  ) +
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
  scale_y_continuous(labels = label_pound(scale = 1e-3, suffix = "K")) +
  labs(
    title    = "Monthly Revenue — Dec 2010 to Dec 2011",
    subtitle = "Strong Q4 seasonality consistent with gift retail cycle",
    x = NULL, y = "Revenue (£K)",
    caption  = "Source: UCI Online Retail Dataset"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r order-volume}
p1 <- ggplot(monthly_rev, aes(x = month_floor, y = n_orders)) +
  geom_col(fill = TEAL, alpha = 0.85) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(labels = comma) +
  labs(title = "Monthly Order Count", x = NULL, y = "Orders") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p2 <- ggplot(monthly_rev, aes(x = month_floor, y = revenue / n_orders)) +
  geom_line(color = ORANGE, linewidth = 1) +
  geom_point(color = ORANGE, size = 2) +
  scale_x_date(date_labels = "%b", date_breaks = "1 month") +
  scale_y_continuous(labels = label_pound()) +
  labs(title = "Average Order Value", x = NULL, y = "AOV (£)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

p1 + p2 +
  plot_annotation(
    title   = "Order Volume vs. Average Order Value",
    caption = "Source: UCI Online Retail Dataset"
  )
```

Order volume and average order value both peak in **November**, reflecting the pre-Christmas
wholesale buying cycle. The drop in December likely reflects fulfilled orders rather than
reduced demand.

---

## 3 · Top Products

```{r top-products-rev}
top_rev <- clean |>
  group_by(stock_code, description) |>
  summarise(
    revenue  = sum(revenue),
    quantity = sum(quantity),
    .groups  = "drop"
  ) |>
  slice_max(revenue, n = 15) |>
  mutate(description = str_to_title(str_trunc(description, 35)))

ggplot(top_rev, aes(x = revenue,
                    y = reorder(description, revenue))) +
  geom_segment(aes(xend = 0, yend = reorder(description, revenue)),
               color = "#CCCCCC", linewidth = 0.8) +
  geom_point(aes(size = quantity), color = NAVY, alpha = 0.85) +
  scale_x_continuous(labels = label_pound(scale = 1e-3, suffix = "K")) +
  scale_size_continuous(labels = comma, range = c(3, 10), name = "Units Sold") +
  labs(
    title    = "Top 15 Products by Revenue",
    subtitle = "Point size proportional to unit volume",
    x = "Total Revenue (£K)", y = NULL,
    caption  = "Source: UCI Online Retail Dataset"
  )
```

```{r top-products-vol}
top_vol <- clean |>
  group_by(stock_code, description) |>
  summarise(
    quantity = sum(quantity),
    revenue  = sum(revenue),
    .groups  = "drop"
  ) |>
  slice_max(quantity, n = 15) |>
  mutate(description = str_to_title(str_trunc(description, 35)))

ggplot(top_vol, aes(x = quantity,
                    y = reorder(description, quantity))) +
  geom_col(aes(fill = revenue), alpha = 0.9) +
  scale_x_continuous(labels = comma) +
  scale_fill_gradient(low = "#AEC6E8", high = NAVY,
                      labels = label_pound(scale = 1e-3, suffix = "K"),
                      name = "Revenue (£K)") +
  labs(
    title    = "Top 15 Products by Unit Volume",
    subtitle = "Fill color shows revenue — high volume ≠ high revenue",
    x = "Total Units Sold", y = NULL,
    caption  = "Source: UCI Online Retail Dataset"
  )
```

The revenue and volume rankings diverge meaningfully — high-unit products are often
low-price consumables while top-revenue products tend to be higher-value decorative items.
This split is worth watching in the velocity section below.

---

## 4 · Geographic Distribution

```{r geo-revenue}
geo <- clean |>
  group_by(country) |>
  summarise(
    revenue    = sum(revenue),
    n_orders   = n_distinct(invoice_no),
    n_customers= n_distinct(customer_id, na.rm = TRUE),
    .groups    = "drop"
  ) |>
  mutate(
    uk_flag = country == "United Kingdom",
    rev_share = revenue / sum(revenue)
  ) |>
  arrange(desc(revenue))

# Ex-UK breakdown
non_uk <- geo |>
  filter(!uk_flag) |>
  slice_max(revenue, n = 12)

p_uk <- ggplot(geo |> mutate(label = if_else(uk_flag, "UK", "International")),
               aes(x = "", y = revenue, fill = label)) +
  geom_col(width = 1, color = "white") +
  coord_polar("y") +
  scale_fill_manual(values = c("UK" = NAVY, "International" = TEAL)) +
  labs(title = "UK vs. International Revenue", fill = NULL) +
  theme_void(base_size = 11) +
  theme(
    plot.title   = element_text(face = "bold", hjust = 0.5, color = NAVY),
    legend.position = "bottom"
  ) +
  geom_text(
    aes(label = percent(rev_share, 1)),
    position = position_stack(vjust = 0.5),
    color = "white", fontface = "bold", size = 4
  )

p_intl <- ggplot(non_uk, aes(x = revenue,
                              y = reorder(country, revenue))) +
  geom_col(fill = TEAL, alpha = 0.85) +
  scale_x_continuous(labels = label_pound(scale = 1e-3, suffix = "K")) +
  labs(title = "Top International Markets (ex-UK)",
       x = "Revenue (£K)", y = NULL)

p_uk + p_intl +
  plot_annotation(
    title   = "Geographic Revenue Distribution",
    caption = "Source: UCI Online Retail Dataset"
  )
```

```{r geo-table}
geo |>
  slice_max(revenue, n = 10) |>
  mutate(
    revenue   = label_pound()(revenue),
    rev_share = percent(rev_share, 0.1),
    n_orders  = comma(n_orders)
  ) |>
  select(Country = country, Revenue = revenue,
         `Share` = rev_share, Orders = n_orders,
         Customers = n_customers) |>
  kbl(caption = "Top 10 Markets by Revenue") |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = FALSE)
```

---

## 5 · Customer Behavior

```{r customer-behavior}
cust <- clean |>
  filter(!is.na(customer_id)) |>
  group_by(customer_id) |>
  summarise(
    n_orders  = n_distinct(invoice_no),
    revenue   = sum(revenue),
    avg_order = revenue / n_orders,
    first_purchase = min(date),
    last_purchase  = max(date),
    .groups   = "drop"
  ) |>
  mutate(
    segment = case_when(
      n_orders == 1              ~ "One-Time",
      n_orders <= 3              ~ "Occasional (2–3)",
      n_orders <= 10             ~ "Regular (4–10)",
      TRUE                       ~ "Frequent (11+)"
    ),
    segment = factor(segment, levels = c("One-Time","Occasional (2–3)",
                                         "Regular (4–10)","Frequent (11+)"))
  )

p_seg <- cust |>
  count(segment) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = segment, y = n, fill = segment)) +
  geom_col(alpha = 0.88, show.legend = FALSE) +
  geom_text(aes(label = paste0(comma(n), "\n", percent(pct, 1))),
            vjust = -0.3, size = 3.2, fontface = "bold") +
  scale_fill_manual(values = c(PALETTE[1], PALETTE[2], PALETTE[7], PALETTE[4])) +
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Customer Purchase Frequency Segments",
       x = NULL, y = "Customer Count")

p_aov <- ggplot(cust, aes(x = segment, y = avg_order, fill = segment)) +
  geom_boxplot(alpha = 0.75, outlier.alpha = 0.2,
               outlier.size = 1, show.legend = FALSE) +
  scale_fill_manual(values = c(PALETTE[1], PALETTE[2], PALETTE[7], PALETTE[4])) +
  scale_y_continuous(labels = label_pound(), limits = c(0, quantile(cust$avg_order, 0.97))) +
  labs(title = "Average Order Value by Segment",
       x = NULL, y = "Avg Order Value (£)")

p_seg + p_aov +
  plot_annotation(
    title   = "Customer Segmentation Overview",
    caption = "Source: UCI Online Retail Dataset · Outliers above 97th percentile trimmed for readability"
  )
```

Frequent buyers (11+ orders) represent a small share of the customer base but drive
disproportionate revenue. The AOV spread within segments reflects the wholesale nature
of the business — a single "Occasional" buyer may be placing very large orders.

---

## 6 · Sales Velocity — Top 20 Products

Sales velocity measures the rate of change in unit sales across three time horizons.
Positive velocity means a product is gaining momentum; negative means it is declining.

```{r velocity-prep}
# ── Focus on top 20 by total revenue ─────────────────────────────────────────
top20_codes <- clean |>
  group_by(stock_code, description) |>
  summarise(revenue = sum(revenue), .groups = "drop") |>
  slice_max(revenue, n = 20) |>
  pull(stock_code)

# Weekly and monthly aggregates for top 20
vel_weekly <- clean |>
  filter(stock_code %in% top20_codes) |>
  mutate(description = str_to_title(str_trunc(description, 30))) |>
  group_by(stock_code, description, week) |>
  summarise(units = sum(quantity), .groups = "drop")

vel_monthly <- clean |>
  filter(stock_code %in% top20_codes) |>
  mutate(description = str_to_title(str_trunc(description, 30))) |>
  group_by(stock_code, description, month_floor) |>
  summarise(units = sum(quantity), revenue = sum(revenue), .groups = "drop")

# ── WoW, MoM, YoY for the most recent available period ───────────────────────
last_week    <- max(vel_weekly$week)
prev_week    <- last_week - weeks(1)
last_month   <- max(vel_monthly$month_floor)
prev_month   <- last_month %m-% months(1)
prev_year_m  <- last_month %m-% months(12)

velocity_summary <- vel_weekly |>
  filter(week %in% c(last_week, prev_week)) |>
  pivot_wider(names_from = week, values_from = units,
              values_fill = 0, names_prefix = "w_") |>
  rename(units_this_week = 3, units_prev_week = 4) |>
  mutate(wow = (units_this_week - units_prev_week) /
                 (units_prev_week + 1)) |>
  left_join(
    vel_monthly |>
      filter(month_floor %in% c(last_month, prev_month)) |>
      pivot_wider(names_from = month_floor, values_from = units,
                  values_fill = 0, names_prefix = "m_") |>
      rename(units_this_month = 3, units_prev_month = 4) |>
      mutate(mom = (units_this_month - units_prev_month) /
                     (units_prev_month + 1)) |>
      select(stock_code, mom, units_this_month, units_prev_month),
    by = "stock_code"
  ) |>
  left_join(
    vel_monthly |>
      filter(month_floor %in% c(last_month, prev_year_m)) |>
      pivot_wider(names_from = month_floor, values_from = units,
                  values_fill = 0, names_prefix = "y_") |>
      rename(units_this_year = 3, units_prev_year = 4) |>
      mutate(yoy = (units_this_year - units_prev_year) /
                     (units_prev_year + 1)) |>
      select(stock_code, yoy),
    by = "stock_code"
  ) |>
  mutate(across(c(wow, mom, yoy), ~ replace_na(., 0)))
```

```{r velocity-chart}
# ── Heatmap-style velocity table ──────────────────────────────────────────────
vel_long <- velocity_summary |>
  select(description, wow, mom, yoy) |>
  pivot_longer(cols = c(wow, mom, yoy),
               names_to = "period",
               values_to = "change") |>
  mutate(
    period = factor(period,
                    levels = c("wow","mom","yoy"),
                    labels = c("Week over Week","Month over Month","Year over Year")),
    change_capped = pmax(pmin(change, 2), -2)
  )

ggplot(vel_long, aes(x = period,
                     y = reorder(description, change[period == "Month over Month"]),
                     fill = change_capped)) +
  geom_tile(color = "white", linewidth = 0.5) +
  geom_text(
    aes(label = if_else(abs(change) > 5,
                        paste0(ifelse(change > 0, "+", ""), round(change * 100), "%"),
                        paste0(ifelse(change > 0, "+", ""), round(change * 100), "%"))),
    size = 2.8, fontface = "bold",
    color = if_else(abs(vel_long$change_capped) > 1.2, "white", "#333333")
  ) +
  scale_fill_gradient2(
    low      = RED,
    mid      = "white",
    high     = TEAL,
    midpoint = 0,
    limits   = c(-2, 2),
    labels   = percent,
    name     = "% Change\n(capped ±200%)"
  ) +
  labs(
    title    = "Sales Velocity Heatmap — Top 20 Products",
    subtitle = paste0("Most recent periods: WoW ending ",
                      format(last_week, "%b %d"),
                      " · MoM ending ", format(last_month, "%b %Y"),
                      " · YoY ending ", format(last_month, "%b %Y")),
    x = NULL, y = NULL,
    caption = "Green = gaining momentum · Red = declining · Values are % change vs. prior period"
  ) +
  theme(axis.text.x = element_text(face = "bold"))
```

```{r velocity-table}
velocity_summary |>
  mutate(
    wow_arrow = case_when(wow >  0.05 ~ "▲", wow < -0.05 ~ "▼", TRUE ~ "→"),
    mom_arrow = case_when(mom >  0.05 ~ "▲", mom < -0.05 ~ "▼", TRUE ~ "→"),
    yoy_arrow = case_when(yoy >  0.05 ~ "▲", yoy < -0.05 ~ "▼", TRUE ~ "→"),
    WoW = paste0(wow_arrow, " ", ifelse(wow >= 0, "+", ""), percent(wow, 1)),
    MoM = paste0(mom_arrow, " ", ifelse(mom >= 0, "+", ""), percent(mom, 1)),
    YoY = paste0(yoy_arrow, " ", ifelse(yoy >= 0, "+", ""), percent(yoy, 1))
  ) |>
  select(Product = description,
         `This Week` = units_this_week,
         `Prev Week` = units_prev_week,
         WoW, MoM, YoY) |>
  arrange(desc(`This Week`)) |>
  kbl(caption = "Sales Velocity Summary — Top 20 Products") |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) |>
  column_spec(4, color = if_else(
    str_starts(velocity_summary |> arrange(desc(units_this_week)) |> pull(wow) |>
                 (\(x) ifelse(x >= 0, "+", "-"))(), "\\+"), TEAL, RED)) |>
  column_spec(5, color = if_else(
    str_starts(velocity_summary |> arrange(desc(units_this_week)) |> pull(mom) |>
                 (\(x) ifelse(x >= 0, "+", "-"))(), "\\+"), TEAL, RED))
```

---

## 7 · Predictive Demand Forecasting

Two approaches are presented: a **rolling average forecast** for operational use,
and an **exponential smoothing model** for technical validation.

### 7a · Manager View — 4-Week Rolling Forecast

The rolling forecast uses each product's recent sales rate to project the next
four weeks. This is the number a purchasing manager should use for weekly order planning.

```{r rolling-forecast}
# ── 4-week rolling average → 4-week forward projection ───────────────────────
rolling_forecast <- vel_weekly |>
  arrange(stock_code, week) |>
  group_by(stock_code, description) |>
  slice_tail(n = 8) |>                      # last 8 weeks of actuals
  summarise(
    avg_weekly_units  = mean(units),
    sd_weekly_units   = sd(units),
    last_4wk_units    = sum(tail(units, 4)),
    prev_4wk_units    = sum(head(tail(units, 8), 4)),
    .groups           = "drop"
  ) |>
  mutate(
    proj_4wk_units    = round(avg_weekly_units * 4),
    proj_low          = round(pmax(0, (avg_weekly_units - sd_weekly_units) * 4)),
    proj_high         = round((avg_weekly_units + sd_weekly_units) * 4),
    momentum          = (last_4wk_units - prev_4wk_units) / (prev_4wk_units + 1),
    order_signal      = case_when(
      momentum >  0.15 ~ "📈 Increase order",
      momentum < -0.15 ~ "📉 Reduce order",
      TRUE             ~ "➡ Maintain order"
    )
  ) |>
  arrange(desc(proj_4wk_units))

rolling_forecast |>
  mutate(
    avg_weekly_units = round(avg_weekly_units, 1),
    proj_range       = paste0(proj_low, " – ", proj_high),
    momentum         = percent(momentum, 1)
  ) |>
  select(
    Product          = description,
    `Avg Wkly Units` = avg_weekly_units,
    `Proj 4-Wk Units`= proj_4wk_units,
    `Range (±1 SD)`  = proj_range,
    `4wk Momentum`   = momentum,
    `Order Signal`   = order_signal
  ) |>
  kbl(caption = paste0("4-Week Demand Projection — Generated ",
                       format(Sys.Date(), "%B %d, %Y"))) |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) |>
  column_spec(6, bold = TRUE)
```

::: {.callout-tip}
## How to use this table
- **Proj 4-Wk Units** — the expected demand volume for the next four weeks at current run rate
- **Range** — one standard deviation above and below the projection; order to the high end if storage permits
- **Order Signal** — based on whether the last 4 weeks ran above or below the prior 4 weeks
:::

### 7b · Model View — Exponential Smoothing Forecast

For the top 6 products by revenue, an ETS (Error, Trend, Seasonal) model is fitted to
the weekly time series. Confidence intervals are shown at the 80% and 95% level.

```{r ets-forecast, fig.height=10}
top6_codes <- clean |>
  group_by(stock_code, description) |>
  summarise(revenue = sum(revenue), .groups = "drop") |>
  slice_max(revenue, n = 6) |>
  pull(stock_code)

# Build a complete weekly grid per product (fill 0 for missing weeks)
all_weeks <- tibble(week = seq(
  floor_date(min(clean$date), "week"),
  floor_date(max(clean$date), "week"),
  by = "1 week"
))

forecast_plots <- map(top6_codes, function(code) {
  desc <- clean |>
    filter(stock_code == code) |>
    pull(description) |>
    unique() |>
    first() |>
    str_to_title() |>
    str_trunc(30)

  prod_weekly <- vel_weekly |>
    filter(stock_code == code) |>
    right_join(all_weeks, by = "week") |>
    arrange(week) |>
    mutate(units = replace_na(units, 0))

  ts_data <- ts(prod_weekly$units, frequency = 52)

  fit <- tryCatch(
    ets(ts_data, model = "ZZZ"),
    error = function(e) ets(ts_data, model = "ANN")
  )

  fc <- forecast(fit, h = 4, level = c(80, 95))

  fc_df <- tibble(
    week   = max(prod_weekly$week) + weeks(1:4),
    mean   = as.numeric(fc$mean),
    lo80   = as.numeric(fc$lower[, 1]),
    hi80   = as.numeric(fc$upper[, 1]),
    lo95   = as.numeric(fc$lower[, 2]),
    hi95   = as.numeric(fc$upper[, 2])
  ) |>
    mutate(across(c(mean, lo80, hi80, lo95, hi95), ~ pmax(., 0)))

  # Last 16 weeks of actuals for context
  actuals_plot <- prod_weekly |> slice_tail(n = 16)

  ggplot() +
    geom_ribbon(data = fc_df,
                aes(x = week, ymin = lo95, ymax = hi95),
                fill = NAVY, alpha = 0.12) +
    geom_ribbon(data = fc_df,
                aes(x = week, ymin = lo80, ymax = hi80),
                fill = NAVY, alpha = 0.22) +
    geom_line(data = actuals_plot,
              aes(x = week, y = units),
              color = "#555555", linewidth = 0.9) +
    geom_line(data = fc_df,
              aes(x = week, y = mean),
              color = NAVY, linewidth = 1, linetype = "dashed") +
    geom_point(data = fc_df,
               aes(x = week, y = mean),
               color = NAVY, size = 2.5) +
    labs(
      title    = desc,
      subtitle = paste0("ETS(", paste(fit$components[1:3], collapse=","), ")"
                        , " · MAPE: ",
                        round(accuracy(fit)["Training set","MAPE"], 1), "%"),
      x = NULL, y = "Units / Week"
    )
})

wrap_plots(forecast_plots, ncol = 2) +
  plot_annotation(
    title    = "ETS Demand Forecast — Top 6 Products (4-Week Horizon)",
    subtitle = "Dashed line = point forecast · Shaded bands = 80% and 95% confidence intervals",
    caption  = "Model: Exponential Smoothing (ETS) fitted per product · Source: UCI Online Retail Dataset"
  )
```

```{r ets-summary-table}
# Summary table of model fit quality
map_dfr(top6_codes, function(code) {
  desc <- clean |>
    filter(stock_code == code) |>
    pull(description) |> first() |> str_to_title() |> str_trunc(35)

  prod_weekly <- vel_weekly |>
    filter(stock_code == code) |>
    right_join(all_weeks, by = "week") |>
    arrange(week) |>
    mutate(units = replace_na(units, 0))

  ts_data <- ts(prod_weekly$units, frequency = 52)
  fit  <- tryCatch(ets(ts_data, model = "ZZZ"),
                   error = function(e) ets(ts_data, model = "ANN"))
  fc   <- forecast(fit, h = 4)
  acc  <- accuracy(fit)

  tibble(
    Product      = desc,
    Model        = paste0("ETS(", paste(fit$components[1:3], collapse=","), ")"),
    MAPE         = round(acc["Training set","MAPE"], 1),
    `Wk1 Proj`   = round(fc$mean[1]),
    `Wk2 Proj`   = round(fc$mean[2]),
    `Wk3 Proj`   = round(fc$mean[3]),
    `Wk4 Proj`   = round(fc$mean[4])
  )
}) |>
  kbl(caption = "ETS Model Fit & 4-Week Forward Projections by Product") |>
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE) |>
  column_spec(3, bold = TRUE,
              color = if_else(
                map_dbl(top6_codes, function(code) {
                  prod_weekly <- vel_weekly |> filter(stock_code == code) |>
                    right_join(all_weeks, by = "week") |>
                    mutate(units = replace_na(units, 0))
                  fit <- tryCatch(
                    ets(ts(prod_weekly$units, frequency = 52), model = "ZZZ"),
                    error = function(e) ets(ts(prod_weekly$units, frequency = 52), "ANN"))
                  accuracy(fit)["Training set","MAPE"]
                }) < 20, TEAL, ORANGE))
```

::: {.callout-note}
## Reading the MAPE column
**MAPE** (Mean Absolute Percentage Error) measures average forecast error as a percentage of actuals.
Under 20% is generally acceptable for weekly retail demand. Higher values indicate
products with irregular or highly seasonal demand patterns where simple ETS models
have limited predictive power.
:::

---

## 8 · Key Takeaways

```{r takeaways}
top_prod_name <- top_rev |> slice_max(revenue, n = 1) |> pull(description)
top_country   <- geo |> filter(!uk_flag) |> slice_max(revenue, n = 1) |> pull(country)
pct_one_time  <- cust |> summarise(p = mean(segment == "One-Time")) |> pull(p)
top_signal    <- rolling_forecast |> filter(order_signal == "📈 Increase order") |>
                   slice_max(proj_4wk_units, n = 1) |> pull(description)
```

- **Seasonality is the dominant revenue driver.** Q4 dominates; inventory and staffing should
  be planned around a November peak.
- **`r top_prod_name`** is the top revenue-generating product and should be treated as
  a flagship SKU with preferential stock levels year-round.
- **`r top_country`** is the largest international market outside the UK and merits
  dedicated outreach and localized promotions.
- **`r percent(pct_one_time, 1)` of identified customers bought only once.** Repeat purchase
  conversion is the highest-leverage growth lever available to this business.
- **`r top_signal`** is showing the strongest upward order signal and is a priority
  restock candidate for the next purchasing cycle.

---

*Analysis produced with R `r R.version$major`.`r R.version$minor` ·
ggplot2 · forecast · Quarto · Data: UCI Online Retail Dataset (CC BY 4.0)*
